% !TEX encoding = UTF-8 Unicode
% !TEX TS-program = lualatex
% !BIB TS-program = biber

\documentclass[%
   corpo=12pt, % optional; default:= 10pt
   oneside, % recommended
   tipotesi=scudo,
   mybibliostyle, % only if biblio is typeset with a personal style
  numerazioneromana, % not necessary in a real thesis
   ]{toptesi}
   

\begin{filecontents*}{\jobname.xmpdata}
\Author{Michele Cocca}
\Title{Conversion of FFCS ICE fleet to EV: a data-driven approach}
\Subject{Doctoral dissertations in the SCUDO doctoral school}
\Keywords{PDF\sep
          PDF/A\sep
          ISO 19005\sep
          LaTeX\sep
          PhD Thesis\sep
          Engineering\sep
          SCUDO}
\Publisher{Politecnico di Torino}
\end{filecontents*}
%%%%%%% -----------------------------------------------------------
   
%%%% Use the following package if and only if you want to produce
%%%% an archivable document according to standard PDF/A-1b
%%%% No need to load package imakeidx, because it has already been
%%%% loaded by the specific module toptesi-scudo.
\usepackage[a-1b]{pdfx}
\usepackage[linesnumbered,ruled,norelsize]{algorithm2e}



\newtheorem{definition}{Definition}
%%%%%% Read the English documentation of TOPtesi in order to check
%%%%%% the special attention needed to produce ISO compliant
%%%%%% archivable files
%%%%

\ifPDFTeX
    \usepackage[utf8]{inputenc}% 
    \usepackage[T1]{fontenc}
\fi

\errorcontextlines=9% more information on the console in case of errors

%%%% Specify fonts here; chose one among these fonts by leaving just
%%%% one line without initial comment character.
%%%% With LuaLaTeX or XeLaTeX don't change fonts
\ifPDFTeX % using pdflatex
    \usepackage{lmodern} % Default
    %\usepackage{newtxtext,newtxmath}% Times eXtended for text and math
    %\usepackage{fourier}% Utopia, Helvetica and "monospace = ?"

\else % using lualatex (or xelatex)
% Here we use the Libertinus serif, sans serif, monospaced and math fonts;
% they are alla available with a complete up-to-date TeXLive installation.
% Without specifying any OpenType font, the Latin Modern OpenType ones are
% used by default; try commenting the setting for Libertinus Mono, run with
% LuaLaTeX and see what happens; you might prefer to keep the comment sign
% in this line.
    \usepackage{fontspec}
    \defaultfontfeatures{Ligatures=TeX}
    \setmainfont{Libertinus Serif}
    \setsansfont{Libertinus Sans}
    \setmonofont{Libertinus Mono}[Scale=MatchLowercase]
    \usepackage{unicode-math}% add special math stile option here
                             % for example [style=ISO]
% define one math font 
    \setmathfont{Libertinus Math}%
\fi


\usepackage{kantlipsum,mwe} % to produce dummy text and dummy figures
\usepackage{booktabs}



\makeindex[intoc]% collect material to index

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This conditional code is an example of using a different bibliography
% style from the one predefined by the class.
% The usage of the conditional code (also with a different contents) is
% discouraged, because the predefined numbered bibliography style is the
% one generally used in scientific publications.
% Even if discouraged, it is not forbidden.
\ifmybibstyle 
  \usepackage[autostyle]{csquotes} % necessary for biblatex
  \usepackage[backend=biber,
              style=philosophy-classic,
              scauthors=all,
              sorting=nyt,
              natbib]{biblatex} % LaTeX specific bibliography handler
\fi 
\addbibresource{\jobname.bib}% bibliographic data base(s)
% It is recommended to name a single or the primary .bib file with the same
% name as the thesis master file: the macro \jobname contains that name.
% It is possible lo use a comma separated list of bibliographical databases
% but extreme care must be paid to the fact that all .bib files have
% actually different names, and that the citations key are really distinct
% among alla databases, not simply within a single database.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The following is to be loaded as the end of the preamble if one wants
% to use hyperlinks and/or urls to be typed within the thesis,
% except that after loading hyperref very few commands may be
% issued. One is the \includeonly command with its list of files;
% other packages may be loaded after hyperref, only if their
% documentation says so; some of these critical packages, but they are
% not the only ones, involve Right to Left languages or other
% oriental languages.
%
% Distinguish the hyperref call from the hyperref setup so as
% to avoid option clashes with other packages that may invoke 
% hyperref with different options.

\unless\ifcsname ver@hyperref.sty\endcsname\usepackage{hyperref}\fi
\hypersetup{%
    pdfpagemode={UseOutlines},
    bookmarksopen,
    pdfstartview={FitH},
    colorlinks,
    linkcolor={blue},
    citecolor={blue},
    urlcolor={blue}
  }
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% The \includeonly argument should preferably be written with
%%%% one file name per line, so that by commenting or uncommenting
%%%% some lines a selective compilation may be executed.
\includeonly{%
Chapter1/1_introduction,%
Chapter2/2_datacollection,%
Chapter3/3_datacharact,%
Chapter4/4_cs_comparison,%
Chapter5/5_simulator,
Chapter6/6_4cities,
Chapter7/7_cs_optimization,
Chapter8/8_prediction,
%Chapter9/9_relocation,
Chapter10/10_scalability,
Chapter11/11_conclusion
%Appendix1/appendix1,
%Appendix2/appendix2,%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\tool}{\textit{UMAP}\xspace}
\newcommand{\MGM}[1]{#1}
\newcommand{\removelatexerror}{\let\@latex@error\@gobble}
\newcommand{\reviewed}[1]{{\color{black}{#1}}}
\newcommand{\mc}[1]{{\color{purple}{[mike: #1]}}}
\usepackage[thinlines]{easytable}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}


\ifPDFTeX \usepackage{indentfirst}\fi
\raggedbottom

\begin{document}

% The contents of this ThesisTitlePage environment may be written
% in a configuration file named exactly the same as the thesis main
% file, but with extension .cfg. If similar commands with different
% data are written within this environment, such data prevail on
% those read from the configuration file.
\begin{ThesisTitlePage}
% Use the optional command to set a different School logo
% Its is possible to used this command several times; each time
% a new different  Institution logo  may be added. In general
% just the ScuDo logo is sufficient; for dissertations made in
% cooperation with the University of Turin, its logo may be added
% with a second instance of the \PhGschoolLog statement. With
% dissertations supported by the INRiM, this institution logo may
% be added. Such logos (in PDF format) may be obtained from the
% ScuDo web server.
\PhDschoolLogo{scudo}% Fake logo for this example
%\PhDschoolLogo{Logo-ScuDo-blu} % just the ScuDo logo
%\PhDschoolLogo{Logo-ScuDo-blu,Logo-INRIM} %for dissertations made in cooperation with INRIM
%\PhDschoolLogo{Logo-ScuDo-blu,Logo-INFN} %for dissertations made in cooperation with INFN
%\PhDschoolLogo{Logo-ScuDo-blu,Logo-UniTo} %for dissertations made in cooperation with the University of Turin
% Doctorate course name; mandatory
\ProgramName{Electronic and Telecommunication Engineering}
% Cycle ordinal number; optional.
% You can write 29.th, or 29\ap{th}, or 29\textsuperscript{th}, or ...
\CycleNumber{33.th}
% PhD candidate name; mandatory
\author{Michele Cocca}
% Dissertation title; mandatory
\title{Electric Revolution and\\Free Floating Car Sharing}
% Dissertation subtitle: optional.
% It might be useful only if the actual full title is too long.
\subtitle{A Data Driven Methodology for System Design}
% The supervisor(s) label; optional; default value "Supervisor:".
% You can change it to plural as in this example, where the colon has
% been eliminated.
%\NSupervisor{Supervisor}{Supervisors}
%
% The SupervisorNumber may contain a value such as 0, 1, or any
% number higher than 1. If 0 is specified, no label is typeset
% over the supervisor(s) list; if 1 is specified then the singular
% form is used: if any value higher than 1 is specified, the plural
% form is used.
\SupervisorNumber{1}
% List of supervisors with academic title, name(s), surname(s),
% and function; mandatory
\SupervisorList{%
    Prof.~Marco Mellia, Supervisor\\
    }
% Name of the examining committee: optional. 
% Default value "Doctoral Examination Committee"
%\Nexaminationcommittee{Doctoral examination committee}
% List of the  examining committee members: mandatory if the above label
% is not empty.
\ExaminerList{%
Prof.~A.B., Referee, University of \dots\\
Prof.~C.D., Referee, University of \dots\\
Prof.~E.F., University of \dots\\
Prof.~G.H., University of \dots\\
Prof.~I.J., University of \dots}
% Name of the institution where the examination takes place; optional.
% Default value: "Politecnico di Torino"
%\Nlocation{Politecnico di Torino}
% Examination date: mandatory, although the way to write it is free.
\ExaminationDate{\today}
% Disclaimer with signature; optional. Default text as
% in the following lines. 
\Disclaimer{%
\noindent I hereby declare that, the contents and organisation of this dissertation constitute my own original work and does not compromise in any way the rights of third parties, including those relating to the security of personal data.	
}

\end{ThesisTitlePage}
%%%%%%%%%%%%%%%% Everything else necessary in the thesis title
%%%%%%%%%%%%%%%% page and in the copyright page is supplied by
%%%%%%%%%%%%%%%% the default values.
%%%%%%%%%%%%%%%% If you enter an explicit disclaimer, you can
%%%%%%%%%%%%%%%% typeset other material before the disclaimer
%%%%%%%%%%%%%%%% formula; use the necessary spacing on order
%%%%%%%%%%%%%%%% to separate the formula from other text. 
%%%%%%%%%%%%%%%% 
%%%%%%%%%%%%%%%% For example you might want to write the formal
%%%%%%%%%%%%%%%% statement for a particular licence, provided the 
%%%%%%%%%%%%%%%% licence allows Open access; not necessarily all uses
%%%%%%%%%%%%%%%% of the thesis should be allowed, but the minimum
%%%%%%%%%%%%%%%% is the reading access.

%%%%%%%%%%%%%%%% The next two lines are metadata for a normal PDF file.
%%%%%%%%%%%%%%%% For ISO archivable PDF/A-1b metadata, they must
%%%%%%%%%%%%%%%% be entered only in the form used in the file
%%%%%%%%%%%%%%%% named in the filecontents* environment as shown
%%%%%%%%%%%%%%%% at the beginning of this file.

%\subject{How to typeset a doctoral thesis suitable for defence in almost any country and university.}
%\keywords{{pdfLaTeX} {LuaLaTeX} {XeLaTeX} {PhD doctoral programs} {PhD dissertation} {Politecnico di Torino}} 

\summary%\sommario
%This is where you write your abstract \dots\ (Maximum 4000 characters, i.e. maximum two pages in normal sized font, typeset with the thesis layout).
%The abstract environment is also available, but  \texttt{\string\summary} is preferred because it generates an un-numbered chapter. The abstract environment is more suitable for articles and two column typesetting without a separate title page.
Nowadays, the increase of traffic congestions, land consume and pollution emission due to a private car ownership opened the way to shared mobility. One of the most spread implementation of shared mobility is Free Floating Car Sharing (FFCS). It is a car rental model where the users can pick and release the car everywhere within an operative area. The customers can reserve (and return) the vehicle through web-based application. With just a simple tap, the users can unlock and lock the smart vehicle. Usually the provider bills the users only for the time spend driving, with time-minute based fares. All the other costs like petrol, insurance and maintenance are in charge to the provider. 

The flexibility of this service fills the urban mobility offer gap between public transport and private car ownership. Indeed, FFCS allows people to travel and commute faster than common public bus but avoiding all the fixed and variable costs related to private car ownership.

Given the recent market market of the electric vehicles and all the pros those vehicles carry, replace FFCS fleet with electric powered cars may still improve the quality of life in urban centres. The setup and management of an electric FFCS requires ingenuity, in order to minimize the users discomfort due the plugging procedures.

In my thesis, I present a methodology to address, in different cases of studies, all the challenges related to the conversion of combustion engine cars to electric vehicles in FFCS. In particular, the main drivers focus on a profitable and technically sustainable system setup able to guarantee a flexible and appealing mobility service to an increasing customer audience.

In the first part of my thesis, I describe the software I developed in order to scrape from the web real combustion engine FFCS, from two providers: car2go and Enjoy. The car2go data collection lasted from December 2016 to January 2018, collecting more than 27 million users' bookings spread in 23 cities while the Enjoy data collection phase started in May 2017 and lasted until June 2019, recording about 6 million bookings in 6 cities. 

Then, I characterize both datasets in Turin, one of the cities in which both FFCS providers work. I detect the outliers filtering them out from the dataset and I extract geo-temporal users' travel patterns.

After that, I compare the car2go customer's pattern with the one-way and two-way car-sharing system. The results show how users prefer more flexible services like FFCS or one-way car sharing.

Once the data are consolidated, I develop (i) a methodology to place a charging station to a city by looking at users' pattern; (ii) system policies to manage the fleet when the vehicle state of charge may not guarantee a trip; (iii) via an event-based trace-driven simulator able to replicate the recorded trips in an electrified scenario evaluating the feasibility of each configuration. 

Via accurate simulation in Berlin, Milan, Turin and Vancouver, I study different electric FFCS setup. By placing the charging station in the most frequented areas, by offering incentive the users to plug the car when the battery state of charge is below a safety threshold and balancing the spread of poles, it is possible to obtain a sustainable system covering with chaging station only the 8-10~\% of zones


To still reduce the number of charging stations to have a sustainable electric FFCS, I compare several optimization algorithms. The results show how a Genetic Algorithm is able to find a better solution able to shrink the minimum amount of resources to sustain the same mobility demand.

After that, I move my attention to the users' rentals predictability. The main goal is to understand how different open-data sources could impact on the recorded FFCS users' rental. Initially, I compare several time-series forecasts to predict the users' demand in the short and medium-term. The Random Forest regression produce better accuracy and results interpretability. Then I correlate the socio-economics features characterizing each city neighbourhood to FFCS demand and again, the Random Forest regression outperforms other algorithms

Finally, I question the system scalability figuring out several scenarios having increasing demand. I use a model able to synthesize users' demand by looking only at the geo-spatial users' rentals. By varying the electric FFCS setup and simulating the new scenario I point out how a linear increase in the demand intensity requires a fleet sub-linear increase. Finally, I project those considerations in euros proofing how electric FFCS has rooms for economic growth. 

%\ringraziamenti
%tba

%%%%%%%%% If you want these two lists, uncomment the following line
\tablespagetrue
\figurespagetrue %

%%%%%%%%% Table of contents and optionally the tables and figures lists
\allcontents

\mainmatter %all the above is front matter; here begins the main matter

\include{Chapter1/1_introduction}
\include{Chapter2/2_datacollection}
\include{Chapter3/3_datacharact}
\include{Chapter4/4_cs_comparison}
\include{Chapter5/5_simulator}
\include{Chapter6/6_4cities}
\include{Chapter7/7_cs_optimization}
\include{Chapter8/8_prediction}
%\include{Chapter9/9_relocation}
\include{Chapter10/10_scalability}
\include{Chapter11/11_conclusion}
%% Numbered appendices remain in the main matter...
\appendix
\include{Appendix1/appendix1}
%\include{Appendix2/appendix2}



\backmatter% here begins the back matter
% ... otherwise a single appendix may stay here
%\include{References/biblio}

% Do not use this command if you did not prepare a nomenclature
% database by means of the suitable \nomenclature command and its
% arguments, as we did in chapter 2 of this example thesis.
\printnomencl

% In this example we use \nocite{*} in order to typeset the whole
% contents of the bibliographic database. Normally this is not
% necessary and it's better to let biber extract from the database
% only the cited works
%\nocite{*}


\printbibliography[heading=bibintoc]

% Do not use this command if you did not set the \makeindex switch
% in the preamble.

\printindex

\end{document}

