% !TEX root = ../thesis.tex
% !TEX encoding = UTF-8 Unicode
% ******************************* Thesis Appendix A 

\chapter{List Of Publications}
\section{Journal Publications}
\begin{itemize}
	\item \textbf{Cocca, M.}, Giordano, D., Mellia, M., & Vassio, L. (2019). Free floating electric car sharing design: Data driven optimisation. Pervasive and Mobile Computing, 55, 59-75.
	
	\item Alencar, V. A., Rooke, F., \textbf{Cocca, M.}, Vassio, L., Almeida, J., & Vieira, A. B. (2019). Characterizing client usage patterns and service demand for car-sharing systems. Information Systems, 101448.
	
	\item \textbf{Cocca, M.}, Giordano, D., Mellia, M., & Vassio, L. (2019). Free Floating Electric Car Sharing: A Data Driven Approach for System Design. IEEE Transactions on Intelligent Transportation Systems, 20(12), 4691-4703.
	
	\item \textbf{Cocca, M.}, Teixeira, D., Vassio, L., Mellia, M., Almeida, J. M., & Couto da Silva, A. P. (2020). On Car-Sharing Usage Prediction with Open Socio-Demographic Data. Electronics, 9(1), 72.
\end{itemize}



\section{Conference Publications}
\begin{itemize}
	\item Ciociola, A., \textbf{Cocca, M.}, Giordano, D., Mellia, M., Morichetta, A., Putina, A., & Salutari, F. (2017, August). UMAP: Urban mobility analysis platform to harvest car sharing data. In 2017 IEEE SmartWorld, Ubiquitous Intelligence & Computing, Advanced & Trusted Computed, Scalable Computing & Communications, Cloud & Big Data Computing, Internet of People and Smart City Innovation (SmartWorld/SCALCOM/UIC/ATC/CBDCom/IOP/SCI) (pp. 1-8). IEEE.
	
	\item \textbf{Cocca, M.}, Giordano, D., Mellia, M., & Vassio, L. (2018, November). Data driven optimization of charging station placement for EV free floating car sharing. In 2018 21st International Conference on Intelligent Transportation Systems (ITSC) (pp. 2490-2495). IEEE.
	
	\item \textbf{Cocca, M.}, Giordano, D., Mellia, M., & Vassio, L. (2018, June). Free floating electric car sharing in smart cities: Data driven system dimensioning. In 2018 IEEE International Conference on Smart Computing (SMARTCOMP) (pp. 171-178). IEEE.
	
	\item Ciociola, A.,\textbf{Cocca, M.}, Giordano, D., Vassio, L., & Mellia, M. (2020, September). E-Scooter Sharing: Leveraging Open Data for System Design. In 2020 IEEE/ACM 24th International Symposium on Distributed Simulation and Real Time Applications (DS-RT) (pp. 1-8). IEEE.
	
	\item Barulli, M., Ciociola, A., \textbf{Cocca, M.}, Vassio, L., Giordano, D., & Mellia, M. On Scalability of Electric Car Sharing in Smart Cities. In 2020 IEEE International Smart Cities Conference (ISC2) (pp. 1-8). IEEE.
	
\end{itemize}







